Inside Out: Externalizing Assumptions in Data Analysis as Validation Checks

### 2024-12-19 _manuscript/_tex/index.tex
new table results

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

@@

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\usepackage{bookmark}

@@

In data analysis, experienced researchers often rely on their prior
knowledge or domain expertise to quickly assess whether results align
with their expectations. When a result falls outside of this interval,
it prompts the researchers to investigate backwards on the data quality,
the analysis steps, or the assumptions made during the analysis process.
This mental process of where to diagnose unexpected outcomes is often
difficult to trace and discuss in publications. As a result, readers are
typically presented with the final outcomes of the analysis cycle where
the results and expectations are aligned, achieved either by refining
the analysis or updating the expectations based on statistical evidence
\citep{grolemund_cognitive_2014}. These missing pieces of information
provides little guidance for diagnosing issues in the analysis when the
same methodology is applied to a new dataset that produces different
outcomes. Similarly, when researchers with different background
knowledge view results that they find to be unexpected, it becomes
unclear whether discrepancies arise from differing expectations or from
the use of statistical techniques.

@@

The skill of diagnosing unexpected data analysis results is not one that
has received significant attention in the statistics literature. While
the concept of diagnosis is often embedded in model checking or data
visualization techniques, systematic approaches to identifying the root
cause of an unexpected analysis result are typically not presented
\citep{peng2022perspective}. \citet{peng_diagnosing_2021} proposed a
series of exercises for training students in data analysis to diagnose
different kinds of analysis problems such as coding errors or outliers.
They provide a systematic approach involving working backwards from the
analysis result to identify potential causes. There are parallels here
to the concept of debugging and testing in software engineering
\citep{donoghue2021teaching}. For example, \citet{li2019towards} found
that experienced engineers were generally able to identify problems in
code faster than novices, and that the ability to debug code required
knowledge that cut across different domains.

@@

Consider a 30-day step count experiment in public health. Subjects are
instructed to walk at least 8,000 steps each day, with an expected
average of 9,000 steps, tracked by a step counter app. After 30 days, we
review the data and examine the number of steps taken each day. With
data of this nature, we may expect there to be occasional ``low'' days
due to factors such as forgetting to wear their watch or unfavorable
weather conditions limiting outdoor activities. We may also expect
``high'' days recorded after an outdoor hike or intense workout. Given
the requirements of the study, we expect that for a given subject the
average step count would be between \([8500, 9500]\).

To diagnose potential reasons why this outcome expectation might fail,
we can establish a few analysis validation checks in anticipation of
seeing the data. For example, we can check the quantile of the step
count, if more than a third of the days fall below 8,000, or more than
two-thirds exceed 10,000 steps, this could indicate an excess of
low-count or high-count days. Similarly, we may may expect the standard
deviation of the step count not to be overly large. These considerations
yield the following three analysis validation checks that \emph{fails}
when:

@@

\includegraphics{index_files/figure-pdf/fig-step-count-1.pdf}

@@

\includegraphics[width=1\textwidth,height=\textheight]{figures/metric-calc.png}

@@

From the simulated data, the accuracy branch refers to a set of checks'
ability to accurately detect unexpected outcomes while minimizing false
positives and false negatives. While a false positive can raise caution
or skepticism on the data, the presence of both false positives and
false negatives suggest that the checks are overly sensitive or lack
sensitivity to unexpected outcomes.

@@

\includegraphics{index_files/figure-pdf/fig-logic-reg-1.pdf}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.5368}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1053}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0737}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0737}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0947}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1158}}@{}}

@@

In the study of the health effects of outdoor air pollution, one area of
interest is the association between short-term, day-to-day changes in
particulate matter air pollution and daily mortality counts. Substantial
work has been done to study this question and to date, there appears to
be strong evidence of an association between particulate matter less
than 10 \(\mu\)g/m\(^3\) in aerodynamic diameter (PM10) and daily
mortality from all non-accidental causes \citep{samet2000fine}. For our
second example, we use the problem of studying PM10 and mortality along
with data from the National Morbidity, Mortality, and Air Pollution
Study (NMMAPS) to demonstrate how our analysis validation checks
described in Section~\ref{sec-method} can be applied.

@@

\begin{longtable}[]{@{}l@{}}
\caption{A list of checks considered for the generalized linear model of
mortality on PM10 and temperature. The checks are based on the sample
size, correlation between mortality and PM10, correlation between
mortality and temperature, and univariate outlier detection. Multiple
cutoff values are specified for each check to determine a
failure.}\label{tbl-checks}\tabularnewline
\toprule\noalign{}
the check fails if \ldots{} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
the check fails if \ldots{} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Sample size less than or equal to 200 \\
Sample size less than or equal to 400 \\
Sample size less than or equal to 600 \\
Sample size less than or equal to 800 \\
Mortality-PM10 correlation less than -0.03 \\
Mortality-PM10 correlation less than -0.04 \\
Mortality-PM10 correlation less than -0.05 \\
Mortality-PM10 correlation less than -0.06 \\
Mortality-temperature correlation greater than -0.3 \\
Mortality-temperature correlation greater than -0.35 \\
Mortality-temperature correlation greater than -0.4 \\
Mortality-temperature correlation greater than -0.45 \\
Outlier(s) are presented in the variable PM10 \\
Outlier(s) are presented in the variable mortality \\
\end{longtable}

@@

To ensure a reasonable likeness to data that might be used in such an
analysis, we use characteristics of the observed dataset to refine our
simulations. AIC is used to determine the best distribution fit for each
variable with the QQ-plot presented in Figure~\ref{fig-dist-fit} to
evaluate the fit. AIC suggests a negative binomial distribution for
mortality, a beta distribution for PM10 (multiple by 100 to recover the
original scale), and a Weibull distribution for temperature. To include
the potential effect of outliers, we add a single outlier to the data
for both the mortality and PM10 variables.

@@

\includegraphics{index_files/figure-pdf/fig-dist-fit-1.pdf}

@@

\includegraphics{index_files/figure-pdf/unnamed-chunk-8-1.pdf}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.6106}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0885}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0619}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0619}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0796}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0973}}@{}}

@@

>>>>

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

@@

\usepackage[]{natbib}
\bibliographystyle{plainnat}
\usepackage{bookmark}

@@

In data analysis, experienced researchers often rely on their prior
knowledge or domain expertise to quickly assess whether results align
with their expectations. When a result falls outside of this
expectation, it prompts the researchers to investigate backwards on the
data quality, the analysis steps, or the assumptions made during the
analysis process. This mental process of where to diagnose unexpected
outcomes is often difficult to trace and document in publications. As a
result, readers are typically presented with the final outcomes of the
analysis cycle where the results and expectations are aligned, achieved
either by refining the analysis or updating the expectations based on
statistical evidence \citep{grolemund_cognitive_2014}. These missing
pieces of information provide little guidance for diagnosing issues in
the analysis when the same methodology is applied to a new dataset that
produces different outcomes. Similarly, when researchers with different
background knowledge view results that they find to be unexpected, it
becomes unclear whether discrepancies arise from differing expectations
or from the use of statistical techniques.

@@

The skill of diagnosing unexpected data analysis results is not one that
has received significant attention in the statistics literature. While
the concept of diagnosis is often embedded in model checking or data
visualization techniques, systematic approaches to identifying the root
cause of a general unexpected analysis result are typically not
presented \citep{peng2022perspective}. Furthermore, if interesting
information is discovered through model checking or data visualization,
there is no formal way to document such discoveries for the next analyst
to consider. \citet{peng_diagnosing_2021} proposed a series of exercises
for training students in data analysis to diagnose different kinds of
analysis problems such as coding errors or outliers. They provide a
systematic approach involving working backwards from the analysis result
to identify potential causes. There are parallels here to the concept of
debugging and testing in software engineering
\citep{donoghue2021teaching}. For example, \citet{li2019towards} found
that experienced engineers were generally able to identify problems in
code faster than novices, and that the ability to debug code required
knowledge that cut across different domains.

@@

Consider a 30-day step count experiment in a public health setting.
Subjects are instructed to walk at least 8,000 steps each day, with an
expected average of 9,000 steps, tracked by a step counter app. After 30
days, we review the data and examine the number of steps taken each day.
With data of this nature, we may expect there to be occasional ``low''
days due to factors such as forgetting to wear their watch or
unfavorable weather conditions limiting outdoor activities. We may also
expect ``high'' days recorded after an outdoor hike or intense workout.
Given the requirements of the study, we expect that for a given subject
the average step count would be between \([8500, 9500]\).

To diagnose potential reasons why this outcome expectation might fail,
we can establish a few analysis validation checks in anticipation of
seeing the data. For example, we can check the quantile of the step
count, if more than a third of the days fall below 8,000, or more than a
third exceed 10,000 steps, this could indicate an excess of low-count or
high-count days. Similarly, we may may expect the standard deviation of
the step count not to be overly large. These considerations yield the
following three analysis validation checks that \emph{fail} when:

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-step-count-1.pdf}}

@@

\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{figures/metric-calc.png}

@@

From the simulated data, the accuracy branch in
Figure~\ref{fig-metric-calc} refers to a set of checks' ability to
accurately detect unexpected outcomes while minimizing false positives
and false negatives. While a false positive can raise caution or
skepticism about the data, the presence of both false positives and
false negatives suggests that the checks are overly sensitive or lack
sensitivity to unexpected outcomes, respectively.

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-logic-reg-1.pdf}}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.5368}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1053}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.0737}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.0737}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.0947}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1158}}@{}}

@@

In the study of the health effects of outdoor air pollution, one area of
interest is the association between short-term, day-to-day changes in
particulate matter air pollution and daily mortality counts. Substantial
work has been done to study this question and to date, there appears to
be strong evidence of an association between particulate matter less
than 10 \(\mu\)g/m\(^3\) in aerodynamic diameter (PM10) and daily
mortality from all non-accidental causes \citep{samet2000fine}. For our
second example, we use the problem of studying PM10 and mortality along
with data from the National Morbidity, Mortality, and Air Pollution
Study (NMMAPS) to demonstrate how our analysis validation checks
described in Section~\ref{sec-method} can be applied. The dataset is
from New York City, and contains daily PM10, mortality, and temperature
values from 1992--2000.

@@

\begin{longtable}[]{@{}l@{}}
\caption{A list of checks considered for the generalized linear model of
mortality on PM10 and temperature. The checks are based on the sample
size, correlation between mortality and PM10, correlation between
mortality and temperature, and univariate outlier detection. Multiple
cutoff values are specified for each check to determine a
failure.}\label{tbl-checks}\tabularnewline
\toprule\noalign{}
the check fails if \ldots{} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
the check fails if \ldots{} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Sample size less than or equal to 200 \\
Sample size less than or equal to 400 \\
Sample size less than or equal to 600 \\
Sample size less than or equal to 800 \\
Mortality-PM10 correlation less than \$-\$0.03 \\
Mortality-PM10 correlation less than \$-\$0.04 \\
Mortality-PM10 correlation less than \$-\$0.05 \\
Mortality-PM10 correlation less than \$-\$0.06 \\
Mortality-temperature correlation greater than \$-\$0.3 \\
Mortality-temperature correlation greater than \$-\$0.35 \\
Mortality-temperature correlation greater than \$-\$0.4 \\
Mortality-temperature correlation greater than \$-\$0.45 \\
Outlier(s) are presented in the variable PM10 \\
Outlier(s) are presented in the variable mortality \\
\end{longtable}

@@

To ensure a reasonable likeness to data that might be used in such an
analysis, we use characteristics of the observed New York City dataset
to refine our simulations. AIC is used to determine the best
distribution fit for each variable with the QQ-plot presented in
Figure~\ref{fig-dist-fit} to evaluate the fit. AIC suggests a negative
binomial distribution for mortality, a beta distribution for PM10
(multiple by 100 to recover the original scale), and a Weibull
distribution for temperature. To include the potential effect of
outliers, we add a single outlier to the data for both the mortality and
PM10 variables.

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-dist-fit-1.pdf}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/unnamed-chunk-8-1.pdf}}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.6106}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.0885}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.0619}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.0619}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.0796}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.0973}}@{}}

@@

\subsection{subsection}\label{subsection}

\begin{table}
\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabular}{lrrrrrrr}
\toprule
City & \makecell[l]{PM10\\Coefficient} & \makecell[l]{Outcome\\Unexpected} & \makecell[l]{Predicted\\Unexpected} & \makecell[l]{Correlation\\Mortality\\PM10} & \makecell[l]{Correlation\\Mortality\\Temperature} & \makecell[l]{Mortality\\Outlier} & \makecell[l]{PM10\\Outlier}\\
\midrule
Atlanta & -0.0008 & T & T & --0.26 (T) & --0.16 (T) & F & F\\
Austin & -0.0030 & T & T & --0.12 (T) & --0.11 (T) & F & T\\
Baltimore & 0.0018 & F & F & --0.21 (T) & 0.01 (F) & T & T\\
Boston & 0.0019 & F & F & --0.16 (T) & 0.02 (F) & F & T\\
Buffalo & 0.0028 & F & F & --0.23 (T) & --0.02 (F) & F & T\\
\addlinespace
Chicago & 0.0011 & F & F & --0.38 (F) & --0.02 (F) & T & T\\
Cincinnati & 0.0011 & F & T & --0.27 (T) & --0.06 (T) & T & T\\
Cleveland & 0.0010 & F & F & --0.30 (F) & --0.02 (F) & T & T\\
Columbus & 0.0004 & F & T & --0.20 (T) & --0.07 (T) & F & T\\
Denver & 0.0010 & F & F & --0.23 (T) & 0.06 (F) & F & T\\
\addlinespace
Detroit & 0.0011 & F & F & --0.30 (T) & 0.04 (F) & F & T\\
Dallas/Fort Worth & 0.0016 & F & T & --0.30 (F) & --0.03 (T) & T & T\\
Honolulu & 0.0006 & F & F & --0.17 (T) & 0.05 (F) & T & T\\
Houston & 0.0007 & F & F & --0.22 (T) & --0.03 (F) & F & T\\
Indianapolis & 0.0014 & F & F & --0.13 (T) & 0.02 (F) & F & T\\
\addlinespace
Kansas City & 0.0022 & F & F & --0.20 (T) & 0.02 (F) & F & T\\
Los Angeles & 0.0011 & F & F & --0.47 (F) & --0.01 (F) & T & T\\
Las Vegas & 0.0008 & F & F & --0.27 (T) & 0.05 (F) & T & T\\
Memphis & -0.0007 & T & T & --0.16 (T) & --0.10 (T) & F & T\\
Miami & -0.0004 & T & F & --0.16 (T) & --0.02 (F) & F & T\\
\addlinespace
Milwaukee & 0.0026 & F & F & --0.22 (T) & 0.09 (F) & F & T\\
Minneapolis/St. Paul & 0.0009 & F & F & --0.30 (F) & --0.01 (F) & T & T\\
New York & 0.0022 & F & F & --0.46 (F) & --0.01 (F) & T & T\\
Oakland & 0.0008 & F & F & --0.28 (T) & 0.04 (F) & F & T\\
Orlando & -0.0008 & T & T & --0.21 (T) & --0.05 (T) & F & T\\
\addlinespace
Philadelphia & 0.0021 & F & F & --0.27 (T) & 0.11 (F) & T & T\\
Phoenix & 0.0009 & F & F & --0.44 (F) & 0.07 (F) & T & T\\
Pittsburgh & 0.0009 & F & T & --0.36 (F) & --0.08 (T) & T & T\\
Riverside & 0.0001 & F & T & --0.27 (T) & --0.11 (T) & T & T\\
Sacramento & 0.0005 & F & F & --0.30 (T) & 0.05 (F) & T & T\\
\addlinespace
Salt Lake City & -0.0004 & T & T & --0.19 (T) & --0.03 (T) & F & T\\
San Antonio & -0.0021 & T & T & --0.22 (T) & --0.16 (T) & F & T\\
San Bernardino & 0.0006 & F & T & --0.28 (T) & --0.09 (T) & T & T\\
San Diego & 0.0011 & F & F & --0.33 (F) & 0.03 (F) & T & T\\
San Jose & 0.0006 & F & F & --0.23 (T) & 0.08 (F) & F & T\\
\addlinespace
Seattle & 0.0003 & F & F & --0.24 (T) & 0.06 (F) & F & T\\
Santa Ana/Anaheim & 0.0005 & F & T & --0.26 (T) & --0.04 (T) & T & T\\
St. Petersburg & 0.0012 & F & F & --0.31 (F) & 0.01 (F) & F & T\\
Tampa & -0.0003 & T & T & --0.20 (T) & --0.04 (T) & F & T\\
Tucson & 0.0028 & F & F & --0.31 (F) & 0.18 (F) & T & T\\
\bottomrule
\end{tabular}}
\end{table}

### 2024-12-19 index.qmd
new table results

>>>>

## subsection

```{r}
pm10 <- read_csv("data/pm10.csv") |> filter(!is.na(pm10)) |> filter(!is.na(temp))
files <- list.files(path = "data", pattern = "csv", full.names = TRUE)[-1]
pred_res <- files |> map_dfr(function(raw){
  data <- read_csv(raw) |> filter(!is.na(pm10)) |> filter(!is.na(temp))
  res_df <- glm(mortality ~ pm10 + temp, family = "poisson", data = data)$coefficients |>
    as_tibble_row()

  res_df |>
      mutate(
        cor_m_tmp = cor(data$mortality, data$temp),
        cor_m_pm10 = cor(data$mortality, data$pm10),
        cor_tmp_pm10 = cor(data$temp, data$pm10),
        unexpect = !between(pm10, 0, 0.005),
        mort_outlier = any(scale(data$mortality) > 4),
        pm10_outlier = any(scale(data$pm10) > 4),
        lgl_cor_m_tmp = cor(data$mortality, data$temp) > -0.3,
        lgl_cor_m_pm10 = cor(data$mortality, data$pm10) < -0.03,
        .pred = ((mort_outlier &  pm10_outlier) | (lgl_cor_m_tmp)) & (lgl_cor_m_pm10),
        ss = nrow(data)
        )
    })

library(readr)
library(kableExtra)
city_name_map <- read_csv(here::here("data/city_name_map.csv"))
tibble(city = str_remove(files, "data/pm10-") |> str_remove(".csv")) |> bind_cols(pred_res) |>
  left_join(city_name_map) |> 
  filter(city != "data/pm10") |> 
  dplyr::select(cityname, pm10, unexpect, .pred, cor_m_tmp, lgl_cor_m_tmp,
                cor_m_pm10, lgl_cor_m_pm10, mort_outlier, pm10_outlier) |>
  mutate(pm10 = format(round(pm10, 4), nsmall = 4),
         cor_m_tmp = format(round(cor_m_tmp, 2), nsmall = 2),
         cor_m_pm10 = format(round(cor_m_pm10, 2), nsmall = 2),
         across(c(cor_m_pm10, cor_m_tmp), ~str_replace(.x, "-", "--"))) |> 
  mutate(across(c(unexpect, .pred, lgl_cor_m_pm10, lgl_cor_m_tmp, mort_outlier, pm10_outlier), 
                ~ifelse(.x, "T", "F"))) |>
  mutate(cor_m_tmp = paste0(cor_m_tmp, " (", lgl_cor_m_tmp, ")"),
         cor_m_pm10 = paste0(cor_m_pm10, " (", lgl_cor_m_pm10, ")")) |> 
  dplyr::select(-lgl_cor_m_tmp, -lgl_cor_m_pm10) |>
  kable(format = "latex", booktabs = TRUE, escape = F, align = "lrrrrrrr",
        col.names = linebreak(c("City", "PM10\nCoefficient", "Outcome\nUnexpected", "Predicted\nUnexpected", 
                                "Correlation\nMortality\nPM10", "Correlation\nMortality\nTemperature",
                                "Mortality\nOutlier", "PM10\nOutlier"))) |>
  kableExtra::kable_styling(latex_options="scale_down") 
```
